\Title

### 2021-01-26 manuscript/manuscript.tex
Improve the discussion section

This section will demonstrate how gradient-boosted equivalent sources can be
used to interpolate large datasets of gravity data onto a regular grid at
uniform height.
For this purpose, we selected an open-access compilation of ground gravity
surveys over Australia made by \citet{wynne2018} and filtered and referenced to
the WGS84 ellipsoid by \citet{australia_compilation}.
It contains over 1.7 million data points and covers most of the Australian
territory at variable point spacings.
Our goal is to create a 1 arc-minute resolution grid of gravity disturbances at
a constant geometric height of \AustraliaEqlGridHeight{} (the largest height of
observations).

We computed the gravity disturbance by removing the normal gravity of
the WGS84 ellipsoid from the observed gravity data (Fig.~\ref{fig:australia}).
Here, normal gravity was computed at each observation point through the
closed-form formula of \citet{ligotze2001} using the Boule software
\citep{boule2020}.
Finally, we convert the observations to planar Cartesian coordinates by
applying a Mercator projection.

We start the interpolation process by defining a set of block-averaged sources
at a relative depth of \AustraliaEqlDepth{} and a block size of
\SI{1.8}{\kilo\meter}, resulting in a total of \AustraliaEqlNSources{}~point
sources.
The block size was chosen to match the desired resolution of the final grid (1
arc-minute is approximately \SI{1.8}{\kilo\meter} at the equator).
The coefficients of the gradient-boosted equivalent sources are estimated using
a damping equal to \AustraliaEqlDamping{} and a window size of
\AustraliaEqlWindowSize{}, which was chosen in order to limit the amount of
computer memory needed to store the Jacobian matrix to under 10 Gigabytes.
Finally, we used estimated source coefficients to predict the values of the
gravity disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid.
Fig.~\ref{fig:australia} shows the original data distribution and the
interpolated regular grid.
Grid points that are further than \SI{50}{\kilo\meter} from the nearest data
point are masked to avoid unrealistic extrapolations.

The resulting grid preserves the high resolution of the original data while
avoiding aliasing artifacts because to the block averaging.
Some parts of the grid are smoother and with reduced amplitude (e.g., some
southwestern parts), which is expected from the upward continuation that was
performed to have the grid at a constant height.
On a modest workstation with 16 cores and 16 Gigabytes of RAM,
estimating the \AustraliaEqlNSources{} coefficients with gradient-boosting took
$\sim 1.3$ hours and the forward modelling step took $\sim 18$ minutes.

@@

Window size:

In comparison with the non-boosted equivalent sources, we can see that the
gradient-boosted ones produce slightly less accurate results due to not being
able to achieve the global minimum of the least-squares problem, but they
perform faster.
The reduction of the accuracy might be due to an oversimplification of the
least-squares problem, and the increase of the computational time might be
generated by the great number of iterations required to fit the sources.
As the windows gets larger, the accuracy starts increasing because more data
points are included into the fitting process of the source coefficients, while
the fitting process takes less time due to a reduction of the number of
iterations.
When using gradient-boosted equivalent sources we can conclude that we want to
maximize the window size as much as possible.
The only limitation to do so is to generate Jacobian matrices larger than the
available memory.
Therefore we recommend using the largest window that generates Jacobian
matrices that could fit in the available memory.

Overlap:

We can then conclude that using overlap values between 40\% and 70\% generate
a balance between predictions accuracy and computational time needed to fit the
source coefficients.
This corroborates that our naive choice of 50\% is good enough for producing
accurate predictions in reasonable times.

If the grid will have a much higher resolution than the block spacing, the
equivalent sources will not be able to reproduce the high frequency components
of the data.
Therefore we recommend setting a block spacing that matches the resolution of
the final grid.

>>>>

Our final goal is to show how gradient-boosted equivalent sources can be used
to interpolate a very large dataset of gravity data into a regular grid.
We selected a compilation of gravity surveys over Australia made by
\citet{wynne2018}.
It consists in more than 1.7 million data points that cover most part of the
Australia territory obtained through observations on ground.
First we compute the gravity disturbance by removing the normal gravity from
the observed gravity data (Fig.~\ref{fig:australia}).
The normal gravity is computed on each observation point through the
closed-form formula given by \citet{ligotze2001} and using the WGS84 ellipsoid
as reference.
Then we obtain planar coordinates of the observation points by applying
a Mercator projection.

We start the interpolation process by defining a set of block-averaged sources
at a relative depth of \AustraliaEqlDepth{} and a block spacing of
\SI{1.8}{\kilo\meter}.
These parameters create \AustraliaEqlNSources{}~point sources.
The choice of the block spacing must be done taking into account the desired
resolution of the final grid.
If the grid will have a much higher resolution than the block spacing, the
equivalent sources will not be able to reproduce the high frequency components
of the data.
Therefore we recommend setting a block spacing that matches the resolution of
the final grid.
In this case we will generate a regular grid with a resolution of 1~arc-minute,
which can be approximated by \SI{1.8}{\kilo\meter} for the Earth.

The coefficients of the gradient-boosted equivalent sources are estimated using
a damping equal to \AustraliaEqlDamping{} and a window size of
\AustraliaEqlWindowSize{} in order to limit the amount of memory needed to
store the largest Jacobian matrix to 10GB.

Finally, the equivalent sources are used to predict the values of the gravity
disturbance on a regular grid of
\AustraliaEqlGridNLongitude{}$\times$\AustraliaEqlGridNLatitude{} points at
\AustraliaEqlGridHeight{} above the ellipsoid
(Fig.~\ref{fig:australia}).

@@

From figures~\ref{fig:gradient-boosted-comparison}a
and~\ref{fig:gradient-boosted-comparison}c we can see that the gradient-boosted
equivalent sources produce slightly less accurate results by failing to achieve
the global minimum of the least-squares problem, but they perform faster than
the non-boosted ones.
The reduction of the accuracy might be due to an oversimplification of the
least-squares problem, and the increase of the computational time might be
generated by the great number of iterations required to fit the sources.
As the windows get larger, the accuracy starts increasing because more data
points are included into the fitting process of the source coefficients, while
the fitting process takes less time due to a reduction of the number of
iterations.
When using gradient-boosted equivalent sources we can conclude that is
desirable to maximize the window size as much as possible.
The only limitation to do so is to generate Jacobian matrices larger than the
available memory.
Therefore we recommend using the largest window that generates Jacobian
matrices that could fit in the available memory.

From the results shown in Figures~\ref{fig:gradient-boosted-comparison}b
and~\ref{fig:gradient-boosted-comparison}d we can conclude that using
overlap values between 40\% and 70\% generate a balance between predictions
accuracy and computational time needed to fit the source coefficients.
This corroborates that our naive choice of 50\% is good enough for producing
accurate predictions in reasonable times.
